Ensemble Methods for Robust Feature Selection

### 2016-08-03 paper/paper.tex
on figure too much, replaced combinations
boxplot addded

\usepackage{jmlr2e}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{subcaption}

% Definitions of handy macros can go here

@@

\begin{figure}[!t]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
  \caption{Accuracy}
  \label{fig:combination_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
  \caption{Robustness}
  \label{fig:combination_robustness}
\end{subfigure}
\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
\label{fig:combination_results}
\end{figure}

\begin{figure}[!t]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
  \caption{Accuracy}
  \label{fig:methods_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
  \caption{Robustness}
  \label{fig:methods_robustness}
\end{subfigure}
\caption{Results for the different methods on average on the different combinations. "Average +" is the average method with the normalized sum. When "\& Perf." is indicated the performance was also used to aggregate the weights.}
\label{fig:methods_results}
\end{figure}

@@

  \caption{The features weights for once for only the real features and once for all. In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features. In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all real features, in the red area are the fake multivariate features and in the orange area are the fake univariate features. }
  \label{fig:feature_weights_plot_artificial}
\end{figure}
\begin{figure}[h!]
  \centering
  \caption{The histograms of the feature weights for all used feature selectors on the arcene and artificial data set.}
\end{figure}
The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
All feature selectors achieved similar results for the artificial data set except of SU. SU does not rank iall features with a zero weight which makes SU fully random on this data set. On the contrary the other feature selectors recognize parts of the inherent structure of the data. The univariate features are in general ranked lower than the multivariate features. There seems to be no diffierence in weighting between the real und fake univariate features. However the real multivariate features are ranked significantly higher than the fake multivariate features. As a consequence only multivariate features are selected. The reason why the feature selectors weight the real univariate features this low is that the univariate features do not contribute significantly to the classification. If we use only the real multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$. On the other hand using the real univariate features we only achieve an accuracy of $0.52$. Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
Furthermore the feature seletors were evaluated after how many real features they capture in the $100$ the highest weighted features. RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
% Acknowledgements should go at the end, before appendices and references

@@

>>>>

\usepackage{jmlr2e}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{float}
% Definitions of handy macros can go here

@@

@@

  \caption{The features weights  once for only the real features and once for all. In figure \ref{fig:feature_weights_plot_artificial_only_features} in the green area are the real multivariate features and in the cyan area are the real univariate features. In figure \ref{fig:feature_weights_plot_artificial_all} in the green are all real features, in the red area are the fake multivariate features and in the orange area are the fake univariate features. }
  \label{fig:feature_weights_plot_artificial}
\end{figure}
The weights of the features can be seen in figure \ref{fig:feature_weights_plot_artificial}.
All feature selectors achieved similar results for the artificial data set except of SU. SU does not rank iall features with a zero weight which makes SU fully random on this data set. On the contrary the other feature selectors recognize parts of the inherent structure of the data. The univariate features are in general ranked lower than the multivariate features. There seems to be no diffierence in weighting between the real und fake univariate features. However the real multivariate features are ranked significantly higher than the fake multivariate features. As a consequence only multivariate features are selected. The reason why the feature selectors weight the real univariate features this low is that the univariate features do not contribute significantly to the classification. If we use only the real multivariate features with the same classification function with which the labels were created, we achieve an accuracy of $0.98$. On the other hand using the real univariate features we only achieve an accuracy of $0.52$. Therefore a feature which correlates with other significant features has significantly more impact on the classification of a data point than a uniform feature.
Furthermore the feature seletors were evaluated after how many real features they capture in the $100$ the highest weighted features. RELIEFF achieved the highest precision of $0.5$, SVM RFE achieved $0.48$, then Lasso with $0.24$ and SU with $0$.
% Acknowledgements should go at the end, before appendices and references

@@

\begin{figure}[!b]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
  \caption{Accuracy}
  \label{fig:combination_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
  \caption{Robustness}
  \label{fig:combination_robustness}
\end{subfigure}
\caption{Results for the different combination of feature selectors. RLF and LSO corresponds respectively to RELIEFF and Lasso.}
\label{fig:combination_results}
\end{figure}

\begin{figure}[!h]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_methods.pdf}
  \caption{Accuracy}
  \label{fig:methods_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_methods.pdf}
  \caption{Robustness}
  \label{fig:methods_robustness}
\end{subfigure}
\caption{Results for the different methods on average on the different combinations. "Average +" is the average method with the normalized sum. When "\& Perf." is indicated the performance was also used to aggregate the weights.}
\label{fig:methods_results}
\end{figure}

\subsubsection{Ensemble methods in comparisment to single feature selection}

As we can see in figure \ref{fig:boxplot} the ensemble methods achieve good results on each data set. While single feature selection methods achieve better results in terms of accuracy and robustness on some data sets, they fail on others. The ensemble methods hold their performance for each dataset. On the arcene data set they even achive better results than any single feature selector.

\begin{figure}[H]
  \centering
    \includegraphics[width=\textwidth]{images/boxplot.pdf}
  \caption{The different ensemble methods compared with single feature selectors in comparisment of stability and accuracy.
  The gray area is the accuracy when using no feature selection.}
  \label{fig:boxplot}
\end{figure}

\section{Discussion}
We have shown that ensemble methods can hold on to results of single feauter selectors and are even superior to the tested feature selectors in terms of generality on different data sets. Further knowledge about the weakness and strength of certain feature selectors can exploited to create good ensembles of feature selectors. It it also has to be tested if the ensemble methods we tried in this work, will also work on other data sets.
